Approximation as Differentiation notes

### 2025-02-09 notes.tex
Start on category of families.
Clarify how a functor F: C \to Set is also a functor F: C \to Cat.

>>>>

\section{Overview}

Some notes on the key constructions:
\begin{itemize}
\item Categories of families, special case of Grothendieck construction
\end{itemize}

\section{Definitions}

\subsection{Category of families}

This is the Grothendieck construction for a functor $F: C \to \Cat$, in the special case where $F: C \to
\Set$. (Where we read a $\Set$-valued functor as a $\Cat$-valued functor restricted to discrete categories.)
